Macro Impacts

### 2016-07-07 Macro Impacts Revised.tex
Good shit
Check out 37 and 38

Reviewing a USGS document (Rock Failure and Earthquakes) suggests that $\bar p$ be set at $10^8$. To calculate $\Delta r$, notice that the Earth is initially displaced by $r_X$. The Earth will then collapse back into the hole due to ambient pressure at the speed of sound $\alpha$, yielding a time of collapse $r_X/\alpha$. The speed of the shockwave initially produced by the object is approximately the speed of the object itself. Hence $\Delta r/v_X=r_X/\alpha$. Thus $\Delta r\approx\f{v_X}{\alpha}r_X$. Thus

@@

\Xi&=\pi \f{(\bar p^2\pi \f{v_X^2}{\alpha^2}r_X^2(\lambda+2\mu)-18K^2\sigma_Xv_X^2\rho_{\oplus})^2}{144K^2(\lambda+2\mu)\rho_{\oplus}\bar p^2 \sigma_X v_X^2\lambda_0^2}\,,\\
&=\p{\pi r_X v_X\f{\bar p^2 -18K^2}{12K\alpha\bar p \lambda_0}}^2\,.

@@

Given the relative magnitudes of $\bar p$ and $K^2$,

@@

\Xi&=\p{\f{3\pi r_X v_XK}{2\alpha\bar p \lambda_0}}^2\,,\\
&=\p{\f{K^2}{\lambda+2\mu}}\p{\f{3\pi}{2\bar p\lambda_0}}^2\abs{\td{E}{x}{}}\,.

@@

@@

These lead to the results

>>>>

Using the upper bound for $\Delta r$ from earlier

@@

\Xi&\geq\p{\f{K^2}{\lambda+2\mu}}\p{\f{4\pi}{3\bar p\lambda_0}}^2\abs{\td{E}{x}{}}\,.

@@

Taking $\Delta r$ to be 0, we find

@@

\Xi&\leq\p{\f{K^2}{\lambda+2\mu}}\p{\f{3\pi}{2\bar p\lambda_0}}^2\abs{\td{E}{x}{}}\,.

@@

%Reviewing a USGS document (Rock Failure and Earthquakes) suggests that $\bar p$ be set at $10^8$. To calculate $\Delta r$, notice that the Earth is initially displaced by $r_X$. The Earth will then collapse back into the hole due to ambient pressure at the speed of sound $\alpha$, yielding a time of collapse $r_X/\alpha$. The speed of the shockwave initially produced by the object is approximately the speed of the object itself. Hence $\Delta r/v_X=r_X/\alpha$. Thus $\Delta r\approx\f{v_X}{\alpha}r_X$. Thus
%\begin{align}
%\Xi&=\pi \f{(\bar p^2\pi \f{v_X^2}{\alpha^2}r_X^2(\lambda+2\mu)-18K^2\sigma_Xv_X^2\rho_{\oplus})^2}{144K^2(\lambda+2\mu)\rho_{\oplus}\bar p^2 \sigma_X v_X^2\lambda_0^2}\,,\\
%&=\p{\pi r_X v_X\f{\bar p^2 -18K^2}{12K\alpha\bar p \lambda_0}}^2\,.
%\end{align}
%Given the relative magnitudes of $\bar p$ and $K^2$,
%\begin{align}
%\Xi&=\p{\f{3\pi r_X v_XK}{2\alpha\bar p \lambda_0}}^2\,,\\
%&=\p{\f{K^2}{\lambda+2\mu}}\p{\f{3\pi}{2\bar p\lambda_0}}^2\abs{\td{E}{x}{}}\,.
%\end{align}

@@

These lead to the results, (using my estimation scheme $\Delta r=\f{v_X}{\alpha}r_X$ from earlier, which may be incorrect)
